Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source

### 2018-08-09 main.tex
models
Update on Overleaf.

The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution. That dwarf galaxies efficiently pollute the circumgalactic medium and intergalactic medium (IGM) with metals has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004,Muratov2017,Corlies2018}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}. If there are differences in metal coupling to the ISM, this could potentially impact how metals are driven out of galaxies through galactic winds. This has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations. However, examining this process has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
%It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}. 
% Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations. However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.

@@

The physical processes that drive galactic chemical evolution are complex, driven by the details of stellar feedback, turbulence and diffusion in a multi-phase ISM, and variations in stellar yields with nucleosynthetic source and stellar metallicity. Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging. 
%[list examples of modeling problems]. 
These uncertainties, combined with the difficulty in simulating a fully self-consistent galaxy in detail, motivates this current study. By focusing on a low mass dwarf galaxy, with small size and low star formation rate, we can capture detailed feedback and ISM physics at high resolution, while following individual stars. In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios, for two reasons. First, we would like to build our understanding of galactic chemical evolution from a fundamental level. Second, there is only a severly limited sample of gas-rich dwarf galaxies of this size that we can use for direct observational comparison, and it is computationally infeasible to simulate galaxies of easily observable size in as much detail as done here. This work will be the first of several attempting to bridge this gap. With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and physically motivated sub-grid physics models for lower resolution simulations of more massive galaxies.

@@

\section{Results}
For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy. This galaxy has an average star formation rate of $1.2~\times 10^{-4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.  The galaxy exhibits strong, feedback-driven outflows \citep{Emerick2018b} that eject a significant amount of gas and metals from the galaxy. The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$, where $\eta$ is defined as the mass outflow rate in through a 0.1~$R_{\rm vir}$ annulus centered at 0.25~R$_{\rm vir}$ divided by the 100~Myr averaged SFR. These winds eject 95\% of the metals produced in the galaxy, with 50\% of all metals leaving the virial radius by the end of the simulation time.

@@

\section{Density PDF}
\label{appendix:density PDF}
We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}. We show the mass-weighted PDF ($dm/Mdn$) on the left, and the volume-weighted PDF ($dv/Vdn$) on the right. As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution. The mass-weighted PDF is broad and flat at low densities, with a large tail through to high densities.   The volume weighted PDF is much better described as a multi-component power law. The other phases do also show some log-normality (more for the mass weighted PDFs than the volume weighted PDFs), but all exhibit power-law tails towards higher densities. These deviations from a log-normal may still be the result of grouping together qualitatively different types of ISM gas.

>>>>

The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution. That dwarf galaxies efficiently pollute the circumgalactic medium and intergalactic medium (IGM) with metals has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004,Muratov2017,Corlies2018}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,Bordoloi2014,McQuinn2015}. If there are differences in metal coupling to the ISM, this could potentially impact how metals are driven out of galaxies through galactic winds. This has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations. However, examining this process has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
%It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}. 
% Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations. However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.

@@

The physical processes that drive galactic chemical evolution are complex, driven by the details of stellar feedback, turbulence and diffusion in a multi-phase ISM, and variations in stellar yields with nucleosynthetic source and stellar metallicity. Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging. 
%[list examples of modeling problems]. 
These uncertainties, combined with the difficulty in simulating a fully self-consistent galaxy in detail, motivates this current study. By focusing on a low mass dwarf galaxy, with small size and low star formation rate, we can capture detailed feedback and ISM physics at high resolution, while following individual stars. In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios, for two reasons. First, we would like to build our understanding of galactic chemical evolution from a fundamental level. Second, there is only a limited sample of gas-rich, star forming dwarf galaxies of this size that we can use for direct observational comparison, and it is computationally infeasible to simulate galaxies of easily observable size in as much detail as done here. This work will be the first of several attempting to bridge this gap. With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and physically motivated sub-grid physics models for lower resolution simulations of more massive galaxies.

@@

\section{Results}
For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy. This galaxy has an average star formation rate of $1.2~\times 10^{-4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.  The galaxy exhibits strong, feedback-driven outflows \citep{Emerick2018b} that eject a significant amount of gas and metals from the galaxy. The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$, where $\eta$ is defined as the mass outflow rate in through a 0.1~$R_{\rm vir}$ annulus centered at 0.25~R$_{\rm vir}$ divided by the 100~Myr averaged SFR. These winds eject 96\% of the metals produced in the galaxy, with 50\% of all metals leaving the virial radius by the end of the simulation time.

@@

\section{Density PDF}
\label{appendix:density PDF}
We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}. We show the mass-weighted PDF ($dm/Md\log n$) on the left, and the volume-weighted PDF ($dv/Vd\log n$) on the right. As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution. The mass-weighted PDF is broad and flat at low densities, with a large tail through to high densities.   The volume weighted PDF is much better described as a multi-component power law. The other phases do also show some log-normality (more for the mass weighted PDFs than the volume weighted PDFs), but all exhibit power-law tails towards higher densities. These deviations from a log-normal may still be the result of grouping together qualitatively different types of ISM gas.
